Waving and swaying

### 2013-12-26 Paper/grass.tex
near_christmas

%\documentclass[aps,twocolumn,floatfix,prl]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
\documentclass[aps,preprint,floatfix,prl]{revtex4-1}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{slashbox}
\usepackage{color}
\usepackage{longtable}
\usepackage{array}
\usepackage{dashrule}

@@

\section{The model}
We use a mean field model for the coupling between the flow and the canopy. Assuming strong oscillation in fluid flow is caused by instability of flow
composed of regions experiencing higher drag with in grass and less outside while monami being response of flexible grass to oscillations of fluid flow. We expect stiffness 
of grass to play minor role in development of flow instability. We approximate grasses with stiff cylindrical rod of diameter $d$ and height $h$ with number density $N/m^2$. 
Drag force exerted by the grass is approximated via a continuous body force $\mathbf{f}=-N\mathbf{f_d}$ in the fluid momentum balance as
%We propose a fully coupled model in order to comprehend dynamics of canopy and fluid flow, drag force excerted by grasses is
%taken as an additional body force in momentum equation of fluid. We approximate presence of grass via continuous field whose shape at any location is approximated as averaged 
%shape of grass at that location which can be obtained by assuming grass to be in quasi-equilibrium at any moment.
% and solving force balance and momentum balance for grass  
\begin{equation}
\rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad P+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}
\end{equation}
%\begin{equation}
% \mathbf{f}=-N\mathbf{f_{d}}
%\end{equation}
where $\mathbf{f_{d}}$ is drag force per unit length of grass, $\rho$ the fluid density, $\mathbf{u}$ the velocity, $P$ the pressure, $\mu$ the viscosity and $\mathbf{g}$
the acceleration due to gravity. Drag force itself is modeled as $\mathbf{f_{d}}=C_N \rho\bu_{N}^{2}d\hat{n}+C_{T}\rho\bu_{T}^{2}d\hat{t}$ where 
$C_{N}$ and $C_{T}$ are normal and tangential drag coefficients respectively which are set to zero outside the grass; $\bu_{T}$, $\bu_{N}$ are velocity vector along and
normal to grass while $\hat{t},\hat{n}$ being unit vector along and normal to grass. We expect $C_T \ll C_N$ and take $C_T=0$ for rest of analysis. We further expect $C_N$ to
not change along the height of the grass and take $C_N$ to be constant for further analysis. 
%\begin{equation}
% \mathbf{f_{d}}=C_N \rho\bu_{N}^{2}d\hat{n}+C_{T}\rho\bu_{T}^{2}d\hat{t}
%\end{equation}\

@@

In order to understand frequency and wavelength associated with passage of dominant eddies over grass which are manifestation of hydrodynamic instability associated with mean flow, 
we investigate stability of base flow profile which is obtained by solving steady state solution of equation(1). Considering small perturbations $u, v, p$  associated 
with base profile $U$ and $P$ respectively, momentum and mass balance equation expanded in 1st order of perturbed variable yields.

@@

Where drag coeffient $C_N$ is set zero out side vagetation. Using height $H$ of fluid column and associated advection time H/$U_{0}$, we use following scalaing to non-dimensinlize equation 
of motion
   \[ u = U_{0}\bar{u},\hspace{1cm} y = (H/2)\bar{y}, \hspace{1cm} \text{with}\hspace{2mm} U_{0}=\frac{(dP/dx)H^2}{4\mu} \]
With these scaling along with the use of stream function $\psi$ with $u = \psi_{y}, v= -\psi_x$, equations can be simplified into a single equation.

@@

 R_{e}\left[\psi_{yyt}+\psi_{xxt}+U\left(\psi_{xyy}+\psi_{xxx}\right)-U_{yy}\psi_{x} \right] &=\left[\psi_{yyxx}+\psi_{yyyy}+\psi_{xxxx}+\psi_{xxyy} \right]\\
& + 2D_{drag}U\psi_{y}\delta(y-h)\\
& - 2D_{drag}U_{y}\psi_{y} -2D_{drag}U\psi_{yy}

@@

where $R_{e}= \frac{\rho U_0 H}{2\mu}$ is Reynolds number and $\bar{N_g} = C_N d N_g H/2$ is non-dimensional grass number density and  $D_{drag} = R_{e}\bar{N_{g}}$ is non-dimensional.
Seeking wave solution in form of $\left(u,v,\psi \right)= \left(\hat u, \hat v, \hat\phi \right)e^{ikx+\sigma}$, we get generalized orr-sommerfield equation 

@@

\sigma \left(D^2-k^2\phi \right) &= \frac{1}{R_{e}}\left[D^4\phi -2k^{2}D^2\phi +k^{4}\phi \right]\\
				  & +ikU_{yy}\phi-ikU\left(D^2\phi-k^2\phi \right)\\
 & -\frac{2D_{drag}}{R_{e}}U_{y}\phi_{y}-\frac{2D_{drag}}{R_{e}}U\phi_{yy}+\frac{2D_{drag}}{R_{e}}U\phi_{y}\delta(y-h)

@@

  \includegraphics[scale=0.35]{Instability2}

@@

\begin{figure}[htb!]
  \includegraphics[scale=0.35]{Instability1_free.jpg}
\caption{Critical Reynolds number with no shear stress at top for different grass height as a function of grass number density}
\end{figure}

>>>>

\documentclass[aps,twocolumn,floatfix,prl,10pt]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
%\documentclass[aps,preprint,floatfix,prl]{revtex4-1}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{slashbox}
\usepackage{color}
\usepackage{longtable}
\usepackage{array}
\usepackage{dashrule}

@@

\section{The model}
We use a mean field model for the coupling between the flow and the canopy. Assuming strong oscillation in fluid flow is caused by instability of flow
composed of regions experiencing higher drag with in grass and less outside while monami being response of flexible grass to oscillations of fluid flow. We expect stiffness 
of grass to play minor role in development of flow instability. We approximate grasses with stiff cylindrical rod of diameter $d$ and height $h$ with number density $N_g/m^2$. 
Drag force exerted by the grass is approximated via a continuous body force $\mathbf{f}=-N_g\mathbf{f_d}$ in the fluid momentum balance as
%We propose a fully coupled model in order to comprehend dynamics of canopy and fluid flow, drag force excerted by grasses is
%taken as an additional body force in momentum equation of fluid. We approximate presence of grass via continuous field whose shape at any location is approximated as averaged 
%shape of grass at that location which can be obtained by assuming grass to be in quasi-equilibrium at any moment.
% and solving force balance and momentum balance for grass  
\begin{equation}
\rho \left(\bu_{t}+\bu.\grad\bu \right) = -\grad P+\mu\grad^{2}\bu +\mathbf{f}+\rho\mathbf{g}
\end{equation}
%\begin{equation}
% \mathbf{f}=-N\mathbf{f_{d}}
%\end{equation}
where $\mathbf{f_{d}}$ is drag force per unit length of grass, $\rho$ the fluid density, $\mathbf{u}$ the velocity, $P$ the pressure, $\mu$ the viscosity and $\mathbf{g}$
the acceleration due to gravity. Drag force itself is modeled as $\mathbf{f_{d}}=C_N \rho\bu_{N}^{2}d\hat{n}+C_{T}\rho\bu_{T}^{2}d\hat{t}$ where 
$C_{N}$ and $C_{T}$ are normal and tangential drag coefficients respectively which are set to zero outside the grass; $\bu_{T}$, $\bu_{N}$ are velocity vector along and
normal to grass while $\hat{t},\hat{n}$ being unit vector along and normal to grass. We expect $C_T \ll C_N$ and take $C_T=0$ for rest of analysis. We further expect $C_N$ to
not change along the height of the grass and take $C_N$ to be constant for further analysis. 
%\begin{equation}
% \mathbf{f_{d}}=C_N \rho\bu_{N}^{2}d\hat{n}+C_{T}\rho\bu_{T}^{2}d\hat{t}
%\end{equation}\

@@

We perform linear stability analysis of a base state associated with the vegetated flow to gain insight about instability characteristics of flow in presence of grass.
Base state flow can be obtained by solving steady state form of constant pressure gradient driven flow associated with equation(1)
$-\frac{dP}{dx}+\mu\frac{d^2U}{dy^2}+\rho C_N d N_gU^2=0$ with no slip at bottom and zero shear at top of surface. Width of shear layer associated with the base flow can be 
obtained by balancing viscous force and vegetative drag in shear layer along with the balance of shear stress exerted by un-vegetated flow at the tip and total vegetative 
drag in shear layer see figure(1). With these balance we can get the scale of shear layer $\delta \sim H\left(\frac{\rho U_0 H}{\mu} C_N d N_g H\right)^{-1/3}$
where $U_0 = \frac{dP/dxH^2}{\mu}$ is scale for velocity.
  \includegraphics[]{fig1}
\caption{Basic flow profile (left )and model of canopy (bottom) along with variation of shear layer (top center) }
Knowing the scale of shear layer we can systematically investigate its effect on flow instability
by varying grass number density $N_g$ and pressure gradient $\frac{dP}{dx}$. Considering small perturbations $u, v, p$ about the base profile $U$ and $P$
respectively, momentum and mass balance equation expanded in 1st order of perturbed variable yields.

@@

Momentum and mass balance equation can be non-dimensionlize using half channel height $H$, associated advection time H/$U_0$ and velocity $U_0 = \frac{dP/dxH^2}{\mu0}$.
%Using half channel height $H$ of and associated advection time H/$U_{0}$, we use following scaling to non-dimensinlize equation 
%of motion
%   \[ u = U_{0}\bar{u},\hspace{1cm} y = (H/2)\bar{y}, \hspace{1cm} \text{with}\hspace{2mm} U_{0}=\frac{(dP/dx)H^2}{4\mu} \]
With these scaling along with the use of stream function $\psi$ with $u = \psi_{y}, v= -\psi_x$ to satisfy mass balance, momentum and mass balance can be combined 
into a single equation.

@@

Re\left[\del_t+\del_x U \right]\grad^2\phi - U_{yy}\psi_x = \grad^4\psi-\frac{\del}{\del_y}\left(\frac{2D_{drag}}{R_e}U\psi_y\right)
%\begin{split}
% R_{e}\left[\psi_{yyt}+\psi_{xxt}+U\left(\psi_{xyy}+\psi_{xxx}\right)-U_{yy}\psi_{x} \right] &=\left[\psi_{yyxx}+\psi_{yyyy}+\psi_{xxxx}+\psi_{xxyy} \right]\\
%& + 2D_{drag}U\psi_{y}\delta(y-h)\\
%& - 2D_{drag}U_{y}\psi_{y} -2D_{drag}U\psi_{yy}
%\end{split}

@@

where $R_{e}= \frac{\rho U_0 H}{\mu}$ is Reynolds number and $\bar{N_g} = C_N d N_g H$ is non-dimensional grass number density and  $D_{drag} = R_{e}\bar{N_{g}}$ is 
non-dimensional drag. Seeking wave solution in form of $\left(u,v,\psi \right)= \left(\hat u, \hat v, \hat\phi \right)e^{ikx+\sigma}$, we get generalized orr-sommerfield equation 

@@

\left(\sigma+ikU\right) \left(D^2-k^2\right)\phi &= \frac{1}{R_{e}}\left[D^2 -k^{2} \right]^2\phi +ikU_{yy}\phi\\
&-\frac{\del}{\del y}\left(\frac{2D_{drag}}{R_e}U\phi_y\right)
%& -\frac{2D_{drag}}{R_{e}}U_{y}\phi_{y}-\frac{2D_{drag}}{R_{e}}U\phi_{yy}+\frac{2D_{drag}}{R_{e}}U\phi_{y}\delta(y-h)

@@

  \includegraphics[]{Critical_Re_vs_Ng_Grizzle}

@@
